Classifying Protein Secondary Structures through Deep Network Learning

### 2013-12-17 docs/paper.tex
added verification section

\subsection{Deep Networks Consisting of Stacked Autoencoders}
We choose a standard approach to creating a deep network by stacking varying numbers of autoencoders \cite{Hinton} which feed into a set of output units.
An autoencoder is a neural network with a single hidden layer that is trained using backpropagation to reproduce its inputs as outputs.
When there are less hidden units then inputs, the autoencoders enforces a more compact representation of the feature vector.
The process of creating a deep network consists of training a set stacked autoencoders where each successive autoencoder's inputs are the previous autoencoder's hidden layer.

@@

\subsubsection{Output Layer}
Our three classifications are the coarse secondary structures: alpha helix, beta sheet, or loop (known in some of the literature as coil).
We represent each of these possibilities with an output unit, where the highest value of the three output units is chosen in a winner-take-all fashion.
These outputs are attached to the hidden layer of the final autoencoder, and the resultant perceptrons are trained with back propagation.
We use a sigmoid function in all of the hidden and output units.

@@

\subsection{Baseline}
Because the related works in section \ref{subsec:relatedworks} all used domain knowledge in some form, we developed our own baseline model for comparison to our deep network.
The baseline is a standar neural network using a single hidden layer and trained with back propagation.

@@

>>>>

\subsection{Deep Networks Consisting of Stacked Autoencoders}
We choose a standard approach to creating a deep network by stacking varying numbers of autoencoders \cite{Hinton} which feed into a set of output units.
An autoencoder is a neural network with a single hidden layer that is trained using backpropagation to reproduce its inputs as outputs.
When there are less hidden units then inputs, the autoencoders enforces a more compact representation of the feature vector.
The process of creating a deep network consists of training a set stacked autoencoders using stochastic gradient descent where each successive autoencoder's inputs are the previous autoencoder's hidden layer.

@@

\subsubsection{Output Layer}
Our three classifications are the coarse secondary structures: alpha helix, beta sheet, or loop (known in some of the literature as coil).
We represent each of these possibilities with an output unit, where the highest value of the three output units is chosen in a winner-take-all fashion.
These outputs are attached to the hidden layer of the final autoencoder, and the resultant perceptrons are trained with back propagation using stochastic gradient descent.
We use a sigmoid function in all of the hidden and output units.

@@

\subsection{Baseline}
All previous work in section \ref{subsec:relatedworks} used domain knowledge in some form, we developed our own baseline model for comparison to our deep network.
The baseline is a standard neural network using a single hidden layer and trained with back propagation using stochastic gradient descent.

@@

\subsection{Verification}
All code for the baseline neural network and the deep network were verified by hand using small examples (no more than sequences of length greater than 5).
Specifically, we traced examples through our perceptron, standard single hidden layer neural network, autoencoder, and stacked autoencoders.
One detail of note, the small examples that were used for verification consistently required at least 1500 iterations over all the training data in order for the weights to converge.
Therefore, after many hours of debugging, we are confident the functionality of our learners are correct.
